Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-01 neurips-20/cvx-flats.tex
Iterating on comments in the intro.

\raf{6/1/2020: The bigger problem though is the end of my ``general comment'' above.  The intro will be much stronger if we can state the gap --- and that's a general principle which applies to almost any paper/proposal/research statement.  In our case, we need to motivate the challenge of designing/reasoning about consistency, and particularly the work on the prediction dimension.  You'll probably want another paragraph for this bit; maybe you have some text that you cut which addresses this?}
\raf{I'd suggest stating this in this ``gap'' paragraph: ``Previous [] bounds on the [prediction dimension] of a consistent surrogate [] considered one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.''  [Edits in []].}

In supervised machine learning, one often makes predictions about future outcomes by minimizing a surrogate loss on training data.
The use of a surrogate is often necessary for one of two reasons: the target loss does not satisfy some ``niceness'' conditions that we desire, or the goal is to estimate some statistic rather than minimize some target loss.
When given a target loss, a surrogate should yield good statistical guarantees; informally, we want low surrogate risk to imply low target risk.
%A good surrogate should yield bounds on the excess risk so that optimal predictions for the surrogate can be linked to optimal predictions for a target (possibly discrete) loss with bounded excess error, regardless of the underlying data distribution.
%\raft{Style example: ``we want low surrogate risk to mean low target risk.''}
In continuous estimation settings, one typically starts with a statistic of the data they would like to estimate instead of a target loss, such as the conditional expected value or an $\alpha$-quantile.
Here, we generalize consistency to make sense in target loss-less contexts (Definition~\ref{def:consistent-prop}).
%For example, if one wants to estimate the $\alpha$-quantile, they can do so by minimizing pinball loss over their data, but it is often unclear \emph{why} pinball loss is good for this prediction task.
We desire a surrogate to be \emph{consistent}: a precursor to excess risk bounds and rates.
We are particularly interested in consistent \emph{and convex} surrogates
% in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting. 
%We would also like our surrogate losses to be 
that are efficient in the dimension of the prediction, as this is one potential source of significant computational speedup.

@@

Our results make two contributions to this field.
First, after introducing a general definition of consistency (\S~\ref{sec:consis-implies-indir}) which applies to all four settings mentioned above, we show that indirect property elicitation is a necessary condition for consistency in all these settings (Theorem~\ref{thm:consistent-implies-indir-elic}).
This observation suggests property elicitation as a more powerful tool to lower bound the prediction dimension of a consistent surrogate.
\raft{Note: convexity not needed in the first one}
Second, we state a general lower bound on the prediction dimension of consistent \emph{convex} surrogates (Theorem~\ref{thm:cvx-flats}) which generalizes a calibration result of \citet{ramaswamy2016convex} to all four settings, and to our knowledge is the first such bound at this level of generality.

@@

% After reviewing previous work and tools to study consistency (\S~\ref{sec:related-work}), we lay down a new general definition of consistency which can simultaneously capture all four settings mentioned above (\S~\ref{sec:consis-implies-indir}).
% Our main result (\S~\ref{sec:char-convex}, Theorem~\ref{thm:cvx-flats}) provides a necessary condition for
% the existence of consistent convex surrogates in a given dimension $d$.
% This result is closely related to those provided by~\citet[Theorem 16]{ramaswamy2016convex} in the discrete prediction setting; in fact, we show their result is a special case of our main result (Corollary~\ref{cor:fsd-bound}).
% We illustrate our main result with several examples (\S~\raf{examples}), one of which addresses an open question posed by~\citet[Section 8]{frongillo2018elicitation} in the continuous estimation setting.
\raft{FYI: use citet when treating citations as nouns; citep is used when the citation does not participate in the grammar, like: ``That is funny [Noah Alexander Frongillo, personal communication, 5/31/2020].''  Not sure what 'cite' does in this style...}

@@

Theorem~\ref{thm:cvx-flats} also addresses one major open question from~\citte{frongillo2015elicitation,frongillo2018elicitation}\jessiet{which citation?}: \emph{what are lower bounds on convex elicitation complexity?}
While Theorem~\ref{thm:cvx-flats} is a statement about consistent surrogates, the heart of it is actually about indirect property elicitation.
Thus, the result also applies to extend previous results~\citep{frongillo2015elicitation,frongillo2018elicitation} to provide new bounds on elicitation complexity for certain classes of properties in Theorem~\ref{thm:bayes-risk-lower-bound}.

>>>>

\raf{6/1/2020: The bigger problem though is the end of my ``general comment'' above.  The intro will be much stronger if we can state the gap --- and that's a general principle which applies to almost any paper/proposal/research statement.  In our case, we need to motivate the challenge of designing/reasoning about consistency, and particularly the work on the prediction dimension.  You'll probably want another paragraph for this bit; maybe you have some text that you cut which addresses this?}
\raf{I'd suggest stating this in this ``gap'' paragraph: ``Previous [] bounds on the [prediction dimension] of a consistent surrogate [] considered one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.''  [Edits in []].}\jessie{A little unclear on what these comments mean, but I tried to incorporate them, assuming I interpreted them correctly.}

In supervised machine learning, one often makes predictions about future outcomes by minimizing a surrogate loss on training data.
The use of a surrogate is often necessary for one of two reasons: the target loss does not satisfy some ``niceness'' conditions that we desire, or the goal is to estimate some statistic rather than minimize a target loss.
When given a target loss, a surrogate should yield good statistical guarantees; informally, we want low surrogate risk to imply low target risk.
%A good surrogate should yield bounds on the excess risk so that optimal predictions for the surrogate can be linked to optimal predictions for a target (possibly discrete) loss with bounded excess error, regardless of the underlying data distribution.
%\raft{Style example: ``we want low surrogate risk to mean low target risk.''}

Without a target loss, one typically starts with a statistic of the data they would like to estimate instead of a target loss, such as the conditional expected value or an $\alpha$-quantile.
We seek \emph{consistent} surrogates, which typically means the average deviation from the hypothesis and true ``regression function'' converges to 0 in probability.
Consistency is important as it is a precursor to excess risk bounds and rates, and we are particularly interested in consistent \emph{and convex} surrogates
% in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting. 
%We would also like our surrogate losses to be 
that are efficient in the prediction dimension, as this is one potential source of significant computational speedup.
%\jessiet{Adding the following two sentences: is this what you meant?}
%While prediction dimension is a well-studied problem (\S~\ref{subsec:complexity}), previous results bounding prediction dimension only apply within very specific settings.
Previous bounds on the prediction dimension of a consistent surrogate have been considered in isolation in one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.

@@

Our results make two contributions to this field.
First, after introducing a general definition of consistency (\S~\ref{sec:consis-implies-indir}) which applies to all four settings mentioned above, we show that indirect property elicitation is a necessary condition for consistency in all these settings (Theorem~\ref{thm:consistent-implies-indir-elic}).
This observation suggests property elicitation as a more powerful tool to lower bound the prediction dimension of a consistent surrogate.
\raft{Note: convexity not needed in the first one \jessie{Rephrased this next sentence to emphasize this point.}}
Second, when restricting our focus to consistent \emph{convex} surrogates, we state a general lower bound on the prediction dimension (Theorem~\ref{thm:cvx-flats}).
This generalizes a calibration result of \citet{ramaswamy2016convex} to all four settings, and to our knowledge is the first such bound at this level of generality.

@@

% After reviewing previous work and tools to study consistency (\S~\ref{sec:related-work}), we lay down a new general definition of consistency which can simultaneously capture all four settings mentioned above (\S~\ref{sec:consis-implies-indir}).
% Our main result (\S~\ref{sec:char-convex}, Theorem~\ref{thm:cvx-flats}) provides a necessary condition for
% the existence of consistent convex surrogates in a given dimension $d$.
% This result is closely related to those provided by~\citet[Theorem 16]{ramaswamy2016convex} in the discrete prediction setting; in fact, we show their result is a special case of our main result (Corollary~\ref{cor:fsd-bound}).
% We illustrate our main result with several examples (\S~\raf{examples}), one of which addresses an open question posed by~\citet[Section 8]{frongillo2018elicitation} in the continuous estimation setting.
\raft{FYI: use citet when treating citations as nouns; citep is used when the citation does not participate in the grammar, like: ``That is funny [Noah Alexander Frongillo, personal communication, 5/31/2020].''  Not sure what 'cite' does in this style...}\jessiet{Noted, and propogated}

@@

Theorem~\ref{thm:cvx-flats} also addresses one major open question from~\citet{frongillo2015elicitation,frongillo2018elicitation}\jessiet{which citation?}: \emph{what are lower bounds on convex elicitation complexity?}
While Theorem~\ref{thm:cvx-flats} is a statement about consistent surrogates, the heart of it is actually about indirect property elicitation.
Thus, the result also applies to extend previous results~\citep{frongillo2015elicitation,frongillo2018elicitation} to provide new bounds on elicitation complexity for certain classes of properties in Theorem~\ref{thm:bayes-risk-lower-bound}.
